---
title: "p8105_hw5_yc4195.Rmd"
output: github_document
author: "Yimin Chen"
date: "November 08, 2022"
---

```{r settingup, echo=FALSE}
library(tidyverse)
library(patchwork)
library(dplyr)
library(readxl)
library(ggplot2)
library(p8105.datasets)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/"),
    path = str_c("data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

```{r}
homicide_df = 
  read_csv("homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = ","),
    resolve = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "Tulsa,AL")
unsolved = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(unsolved = sum(resolve == "unsolved"),
            total_number = n()) 
unsolved
```
The data set consists of `r nrow(homicide_df)` cases, and `r ncol(homicide_df)`  variables that include the time, place, and nature of the murder, whether an arrest was made, and basic demographic information about each victim.

```{r}
 Baltimore_df =
  unsolved %>% 
  filter(city_state == "Baltimore,MD")

prop.test(
   Baltimore_df %>% pull(unsolved), 
   Baltimore_df %>% pull(total_number)) %>% 
  broom::tidy()

```
The estimated proportion of homicides in Baltimore is 64.6% and its 95% confidence interval is [62.8%, 66.3%].

```{r}
prop_df = unsolved %>% 
  mutate(
    test = map2(.x = unsolved, .y = total_number, ~prop.test(x = .x, n = .y)),
    test = map(test,broom::tidy)
         )  %>% 
  unnest() %>% 
  select(city_state, estimate, conf.low, conf.high) %>%
  arrange(desc(estimate))
plot_df=
  prop_df%>% 
  ggplot(aes(x = reorder(city_state,estimate), y =estimate))+
  geom_point()+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.9, hjust = 1))+
  labs(title = "The estimates and CIs for each city",x = "City", y = "Proportions of unsolved homicides")
plot_df
```

## Problem 3

```{r sim}
set.seed(5000)
estimate_test = function(n=30, mu, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n=n, mean = mu, sd = sigma)
  )
  
  sim_data %>% 
        summarize(t_test =t.test(x,mu = 0, conf.level = 0.95) %>%
        broom::tidy() %>% 
        select(estimate, p.value))
}


sim_test =
  rerun(5000, estimate_test(mu = 0)) %>% 
  bind_rows()%>% 
  mutate(
    mu_hat = pull(t_test,estimate),
    p_value = pull(t_test,p.value)) %>% 
  select(-t_test)

sim_test

sim_test1 =
  tibble(
    mu = c(0,1,2,3,4,5,6)
  ) %>% 
  mutate(
    output_lists = map(.x = mu, ~rerun(5000, estimate_test(n=30,mu = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)%>%
  mutate(
    mu_hat = pull(t_test,estimate),
    p_value = pull(t_test,p.value))%>% 
  select(mu, mu_hat, p_value)

sim_test1
```


```{r }
proportionplot =
  sim_test1 %>% 
  group_by(mu) %>% 
  summarize(total_number = n(),rejected_number = sum(p_value < 0.05)) %>% 
  mutate(proportion = rejected_number / total_number) %>% 
  ggplot(aes(x = mu, y = proportion,color=mu)) +
  geom_point() +
  geom_line()+
  labs(
    title = "Association between effect size and power",
    x = "mu Value",
    y = "Proportion of times the null was rejected "
  ) + 
  theme(plot.title = element_text(hjust = 0.5))
proportionplot
```


The proportion of times the null is rejected increases as mu increases. Therefore, as the size of the effect increases, its power also increases.

```{r }
plot1 =
  sim_test1%>% 
  group_by(mu) %>%
  summarize(avg_muhat = mean(mu_hat)
  ) %>% 
  ggplot(aes(x = mu, y = avg_muhat,color=mu)) + 
  geom_point() +
  geom_line() +
  labs(
    x = "True mu Value",
    y = "Average estimate of mu",
    title = "Total datasets"
  ) + 
  theme(plot.title = element_text(hjust = 0.5))


plot2 =
  sim_test1%>% 
  filter(p_value < 0.05) %>% 
  group_by(mu) %>%
  summarize(
    avg_muhat = mean(mu_hat)
  ) %>% 
  ggplot(aes(x = mu, y = avg_muhat,color=mu)) + 
  geom_point() +
  geom_line() +
  labs(
    x = "True mu Value",
    y = "Average estimate of mu",
    title = "Total rejected datasets"
  ) + 
  theme(plot.title = element_text(hjust = 0.5))
```

```{r patchwork}
plot1 + plot2
```


In the combined plot, we can see when the effect size/true value of mu is small (from 0 to 3), he sample average of mu hat across tests for which the null is rejected was not equal to the true value of mu.However, the average estimate of mu approximates the true mu value when the effect size is between 4 and 6. That is to say, since as the size of the effect increases, its power also increases, and the average estimate of mu gradually approximates or equal to the true mu value. 

